Terrain is a stronger predictor of peat depth than airborne radiometrics in Norwegian landscapes

### 2024-12-05 ms/ms.Rmd
ms: grammer
ms: code and data statement

    *Code and data availability.* Use this to add a statement when having data sets and software code available

@@

None of the models were able to predict peat depth across the study areas with high accuracy (Fig. \@ref(fig:modelMetrics)).
For Skrimfjella the best model achieved a concordance correlation coefficient of 0.3, an R^2^ of 0.34, and a mean absolute error of 60 cm.
For Ørskogfjellet the same values were 0.39, 0.33, and 56 cm, so the best model at Ørskogfjellet was slightly more accurate than the best model at Skrimfjella.
These values were derived from kNNDM spatial cross-validation with 20 folds at Skrimfjella and 10 folds at Ørskogfjellet.

>>>>

    R code used in this study is available at <https://github.com/julienvollering/DSMdepth>. Depth measurements will be archived in a public repository upon publication.

@@

None of the models was able to predict peat depth across the study areas with high accuracy (Fig. \@ref(fig:modelMetrics)).
For Skrimfjella the best model achieved a concordance correlation coefficient of 0.3, an R^2^ of 0.34, and a mean absolute error of 60 cm.
For Ørskogfjellet the same values were 0.39, 0.33, and 56 cm, so the best model at Ørskogfjellet was slightly more accurate than the best model at Skrimfjella.
These values were derived from kNNDM spatial cross-validation with 20 folds at Skrimfjella and 10 folds at Ørskogfjellet.

### 2024-12-05 ms/ms.tex
ms: grammer
ms: code and data statement

None of the models were able to predict peat depth across the study areas with high accuracy (Fig. \ref{fig:modelMetrics}).
For Skrimfjella the best model achieved a concordance correlation coefficient of 0.3, an R\textsuperscript{2} of 0.34, and a mean absolute error of 60 cm.
For Ørskogfjellet the same values were 0.39, 0.33, and 56 cm, so the best model at Ørskogfjellet was slightly more accurate than the best model at Skrimfjella.
These values were derived from kNNDM spatial cross-validation with 20 folds at Skrimfjella and 10 folds at Ørskogfjellet.

@@

\codedataavailability{\emph{Code and data availability.} Use this to add a statement when having data sets and software code available} %% use this section when having data sets and software code available

>>>>

None of the models was able to predict peat depth across the study areas with high accuracy (Fig. \ref{fig:modelMetrics}).
For Skrimfjella the best model achieved a concordance correlation coefficient of 0.3, an R\textsuperscript{2} of 0.34, and a mean absolute error of 60 cm.
For Ørskogfjellet the same values were 0.39, 0.33, and 56 cm, so the best model at Ørskogfjellet was slightly more accurate than the best model at Skrimfjella.
These values were derived from kNNDM spatial cross-validation with 20 folds at Skrimfjella and 10 folds at Ørskogfjellet.

@@

\codedataavailability{R code used in this study is available at \url{https://github.com/julienvollering/DSMdepth}. Depth measurements will be archived in a public repository upon publication.} %% use this section when having data sets and software code available
